Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

maalin$genus <- maaslinwrapper(pseq = pseq.genus,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = "Halapricum.Archaea-")

@@

maalin$lacto.min <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX"),
                taxa = lactotaxa)

maalin$lacto.max  <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = lactotaxa)
```

>>>>

maaslin$genus <- maaslinwrapper(pseq = pseq.genus,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = "Halapricum.Archaea-")

@@

maaslin$lacto.min <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX"),
                taxa = lactotaxa)

maaslin

maaslin$lacto.max  <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = lactotaxa)
```
